---
title: "Assignment-5"
date: "12/3/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Problem 3: (a) Use the K-means method to cluster the prospects dataset. Set the number of clusters to four.How many points are in each cluster? What are cluster means and variances?

```{r kmeans_data, echo=TRUE}
library(readxl)

prospect_data <- read_excel("/Users/Downloads/FAll 2019/IDS-572 DataMining/Assignment_5/prospect.xls")
clust_data <- prospect_data[,-c(1,7)]

# data cleaning
dim(clust_data)

#check if any missing values 
sum(is.na(clust_data))

clust_data_na_removed <- data.frame(na.omit(clust_data))
dim(clust_data_na_removed)
```

```{r kmeans_a, echo=TRUE}
set.seed(123456)

library(dplyr)
glimpse(clust_data_na_removed)

clust_data_na_removed[,3] <- as.factor(clust_data_na_removed[,3])
clust_data_na_removed[,4] <- as.factor(clust_data_na_removed[,4])
clust_data_na_removed[,5] <- as.factor(clust_data_na_removed[,5])
clust_data_na_removed[,6] <- as.factor(clust_data_na_removed[,6])

library(e1071)

kmeans_model <- kproto(clust_data_na_removed,k=4, nstart = 20)

#Size of each cluster
kmeans_model$size
#centroids 
kmeans_model$centers
```

### (b) For each of the four clusters, briefly describe the characteristics of members of that cluster.

```{r part_b_kmeans, echo=TRUE}
```

### (c) What is the best value of k for this data set??

```{r kmeans_part_c,echo=TRUE}
bestkplot <- function(data, nc=25, seed=1234){
  wss <- (nrow(data)-1)*sum(apply(data,2,var))
  
  for (i in 2:nc){
    set.seed(seed)
    wss[i] <- sum(kproto(data, k=i)$withinss)
  }
  
  plot(1:nc, wss, type="b", xlab="Number of Clusters",ylab="Within groups sum of squares")
}

bestkplot(clust_data_na_removed, nc=25) 

# 2-D representation for the clusters

library(cluster)

clusplot(clust_data_na_removed, kmeans_model$cluster, main='2D representation of the Cluster solution',color=FALSE, shade=FALSE,
         labels=2, lines=0,diss = FALSE)
```

**Best value of k should be 5 as it is giving the least dip in sum of square error witihn the groyps**

### (d) What is the Silhouette measure of the clusters obtained by best k in part (c).

```{r kmeans_part_d, echo=TRUE}
library(cluster)
library(factoextra)

set.seed(45453)
k_means_model_best_k <- kproto(clust_data_na_removed, k=5)
#sil_coeff <- silhouette(kmeans_model$cluster, dist(clust_data_na_removed))
sil_coeff <- silhouette(k_means_model_best_k$cluster, dist(clust_data_na_removed))
fviz_silhouette(sil_coeff)
```

**Average silhouette width is 0.04.**